---
title: "ggplot_for_whoi_repo_ver2"
author: "Mary Farina"
date: "10/22/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages

```{r packages}
install.packages('tidyverse') # note on Windows and linux use double quotes
library(tidyverse)
```

## Load NP data


```{r load_data}
#National Parks in California
ca <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/ca.csv") 

#Acadia National Park
acadia <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/acadia.csv")

#Southeast US National Parks
se <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/se.csv")

#2016 Visitation for all Pacific West National Parks
visit_16 <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/visit_16.csv")

#All Nationally designated sites in Massachusetts
mass <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/mass.csv")
```


Start with the California dataset

```{r}

ggplot(data = ca) + 
  geom_point(aes(x=year, y=visitors,color=park_name)) +
  labs(x="Year",y="Visitation",title = 'CA National Park Visitation') +
  theme_bw() +
  theme(legend.title = element_blank())

```


Using the se dataset, make a scatterplot showing visitation to all national parks in the Southeast region with color identifying individual parks.
Change the plot so that color indicates state.
Customize by adding your own title and theme. You can also change the text sizes and angles. Try applying a 45 degree angle to the x-axis. Use your cheatsheet!
In the code below, why isn’t the data showing up?
ggplot(data = se, aes(x = year, y = visitors))


```{r}

ggplot(data = se) + 
  geom_point(aes(x=year, y=visitors,color=state)) +
  labs(x="Year",y="Visitation",title = 'SE National Park Visitation by state') +
  theme_minimal() +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, size=14))

```

# Faceting plots

```{r}
ggplot(data = se) +
  geom_point(aes(x=year, y =  visitors, color = park_name)) +
  facet_wrap(~ state, scales = "free") +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, size=14))
  
```




```{r}
ggplot(data = se) +
  geom_jitter(aes(x=park_name, y =  visitors, color=park_name ), alpha = 0.4, width = 0.1) +
  coord_flip()
  
```


```{r}
ggplot(se) +
  geom_line(aes(x=year, y =  visitors, color=park_name )) +
  theme_bw()
```

#Multiple geoms

```{r}
ggplot(acadia, aes(x=year, y=visitors, color=year)) +
  geom_point() +
  geom_line() +
  geom_smooth() +
  theme_bw()
```

# Bar Charts

```{r}
ggplot(data = visit_16, aes(x=state, y= visitors, fill = park_name)) +
  geom_bar(stat = "identity", position = 'dodge')
```

#Save a ggplot

```{r}
myplot <- ggplot(data = visit_16, aes(x=state, y= visitors, fill = park_name)) +
  geom_bar(stat = "identity", position = 'dodge')

myplot

ggsave("myplot.png", myplot )

```
